Between Subgraph Isomorphism and Maximum Common Subgraph

### 2016-08-30 paper/paper.tex
Needing to restart machine, tmp paper update.

\begin{proposition}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \lessmap t$ then
    $\deg(p) - k \le \deg(t)$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

@@

\end{proof}

@@

\begin{proposition}
    Let $p,q \in V(P)$ and $t,u\in V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) \le \paths(t, u, 2) + k$.
\end{proposition}

>>>>

\begin{proposition}
    \label{prop:deg}
    Let $p$ be a vertex in $P$ and $t$ a vertex in $T$. For both non-induced and induced
    $k$-less-subgraph isomorphisms, if $p \lessmap t$ then
    $\deg(p) - k \le \deg(t)$.
\end{proposition}
\begin{proof}
Let $p$ be a vertex in $P$, and $t$ a vertex in $T$, with $p\mapsto t$. Then by the definition of subgraph isomorphisms, $\deg(p) \le \deg(t)$. Let $P'$ be $P$ less $k$ vertices and $p$ a vertex in $P'$. Then
\[
\deg_{P}(p)-k \le \deg_{P'}(p) \le \deg_{P}(p) \le \deg(t).
\]
\end{proof}

@@

\end{proof}
\begin{figure}
    \begin{center}
        \begin{tikzpicture}{every node/.style={circle, inner sep=1mm}}
            \node[fill=black] (p)  {};
            \node[fill=red] (n1) [above left of = p] {};
            \node[fill=blue] (n2) [above of = p] {};
            \node[fill=blue] (n3) [above right of = p] {};
            \node[fill=green] (q) [above of = n2] {};
            %\path[]
        \end{tikzpicture}
        \caption{Graph that Craig wanted}
        \label{fig:nds}
    \end{center}
\end{figure}

@@

\begin{proposition}
    Let $p,q \in V(P)$ and $t,u\in V(T)$. If $p \lessmap{k} t$ and $q \lessmap{k} u$ then
     $\paths(p, q, 2) - k \le \paths(t, u, 2)$.
\end{proposition}
\begin{proof}
Let $P_{2}$ be the set of all paths of length two between $p$ and $q$,
\begin{align*}
P_{2} = & \{((p,x),(x,q)) : (p,x),(x,q)\in E(P) \} \\
 = & \{((p,x),(x,q)) : x\in N(p) \text{ and } x\in N(q) \} \\
 = & \{((p,x),(x,q)) : x\in N(p)\cap N(q) \} .
\end{align*}
So $\paths(p,q,2) = | N(p)\cap N(q)| \leq deg(p)$.

If we remove up to $k$ vertices from the neighbourhood of $p$, it will impact the intersection of the neighbourhoods of $p$ and $q$, and by Proposition~\ref{prop:deg}, as $p\lessmap{k}t$
\[
|N(p)\cap N(q)| - k \leq deg(p) - k \leq deg(t).
\]
As $|N(p)\cap N(q)|\leq deg(p) \leq |N(t)\cap N(u)|\leq deg(t)$, we have
\[
|N(p)\cap N(q)| - k \leq deg(p) - k\leq |N(t)\cap N(u)|\leq deg(t)
\]
which is
\[
\paths(p, q, 2) - k \leq \paths(t, u, 2).
\]
\end{proof}
